Modal Verification Patterns for Systems

### 2025-06-16 paper.tex
+

\subsection{Nominalization}
Finally, another design point is the question of whether or not resource element assertions must explicitly track
their corresponding context, or if they implicitly pick up their context from where they are used.

>>>>

\subsection{Nominals for Systems Resource Contexts}
Finally, another design point is the question of whether or not resource element assertions must explicitly track
their corresponding context, or if they implicitly pick up their context from where they are used.
